---
title: "Drake Equation Sampling and Plotting"
author: "Your Name"
date: "2025-05-03"
output: html_document
---

## Introduction

The Drake equation is a probabilistic argument used to estimate the number of active, communicative extraterrestrial civilizations in our galaxy. The equation is usually written as:

$$ N = R_* \times f_p \times n_e \times f_l \times f_i \times f_c \times L $$

Where:
- \( R_* \): Average rate of star formation per year in our galaxy.
- \( f_p \): Fraction of those stars that have planetary systems.
- \( n_e \): Number of planets that could potentially support life per star with planets.
- \( f_l \): Fraction of planets that actually develop life.
- \( f_i \): Fraction of planets with life that develop intelligent life.
- \( f_c \): Fraction of intelligent civilizations that develop detectable communication.
- \( L \): Length of time such civilizations release detectable signals.

In this example, we will draw random samples for each parameter and compute \( N \), then plot the distribution of \( N \).

## R Code

```{r setup, include=FALSE}
# Set up the environment
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load necessary libraries
library(ggplot2)
```

```{r}
# Define ranges or means for each parameter and draw random samples
set.seed(123)  # For reproducibility

# Number of samples
n_samples <- 10000

# Parameters: Generate random samples (uniform or normal distributions, as appropriate)
R_star <- runif(n_samples, 1, 10)    # Star formation rate (e.g., 1-10 stars/year)
f_p <- runif(n_samples, 0.1, 0.5)    # Fraction of stars with planets
n_e <- runif(n_samples, 0.1, 2)      # Number of habitable planets per star with planets
f_l <- runif(n_samples, 0.01, 1)     # Fraction of habitable planets with life
f_i <- runif(n_samples, 0.01, 1)     # Fraction of planets with intelligent life
f_c <- runif(n_samples, 0.01, 1)     # Fraction of civilizations that communicate
L <- runif(n_samples, 100, 10000)    # Longevity of civilizations (in years)

# Compute N (Drake equation results)
N <- R_star * f_p * n_e * f_l * f_i * f_c * L
```

```{r, echo=FALSE}
# Plot the distribution of N
ggplot(data.frame(N = N), aes(x = N)) +
  geom_histogram(bins = 50, fill = "blue", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Drake Equation Results",
    x = "Number of Communicative Civilizations (N)",
    y = "Frequency"
  ) +
  theme_minimal()

```